---
title: "Reproducibility review of: Tracking Hurricane Dorian in GDELT and Twitter"
author: "NAME \\orcid{0000-0002-9317-8291}"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  pdf_document:
    toc: false
header-includes:
  - |
    % https://tex.stackexchange.com/questions/445563/ieeetran-how-to-include-orcid-in-tex-pdf-with-pdflatex/445583 (works with pdflatex)
    \usepackage{scalerel}
    \usepackage{tikz}
    \usetikzlibrary{svg.path}
    \definecolor{orcidlogocol}{HTML}{A6CE39}
    \tikzset{
      orcidlogo/.pic={
        \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3    ,256,128z};
        \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                     svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z     M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                     svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88    .7,51.3,88.7,56.8z};
      }
    }
    \newcommand\orcid[1]{\href{https://orcid.org/#1}{\raisebox{0.15 em}{\mbox{\scalerel*{
    \begin{tikzpicture}[yscale=-1, transform shape]
    \pic{orcidlogo};
    \end{tikzpicture}
    }{|}}}}}
    \definecolor{agileblue}{RGB}{0,77,155}
urlcolor: agileblue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r logo, echo = FALSE, message=FALSE, fig.align='center', out.width='0.3\\linewidth', fig.pos='H'}
temp <- tempfile(fileext = ".pdf")
download.file(url = "https://github.com/reproducible-agile/reproducible-agile.github.io/raw/master/public/images/reproducible-AGILE-logo-square.pdf", destfile = temp)
knitr::include_graphics(temp)
```

This report is part of the reproducibility review at the AGILE conference.
For more information see [https://reproducible-agile.github.io/](https://reproducible-agile.github.io/).
This document is published on OSF at OSF LINK HERE.
To cite the report use

> FULL REPORT CITATION HERE

# Reviewed paper

Tracking Hurricane Dorian in GDELT and Twitter
Innocensia Owuor, Hartwig H. Hochmair, Sreten Cvetojevic
https://github.com/InnocensiaO/Tracking-Hurricane-Dorian-in-GDELT-and-Twitter

# Summary

In principle, the authors do a commendable job in providing all code and all data that can be provided (given platform terms of service). The reproduction is made more difficult by the absence of a documentation that explains what the scripts are doing, and in which order they are to be run. While this can be inferred through some research and trial and error, and the paper's boxplots were successfully reproduced, the maps cannot be reproduced with the materials provided. The encountered error in one script might be due to the reviewer's computational environment. I was not able to fix it within a reasonable amount of time, which is likely to be different for a more skilled reviewer. 

\clearpage

# Reproducibility reviewer notes

The materials on GitHub do not have an explicit license -> public domain?

## Data 

Twitter data
The data collection and preprocessing is not reproducible, because the exact query is not given (study area?) and bot removal was conducted via external API. However, with all used Twitter IDs provided, I was able to hydrate 90% (with Hydrator v0.3) of the input data. This shows how useful and important it is to provide at least the Tweet IDs. 

GDELT data
The query to recreate it is given, but it might cost a fee to access the data. If I understood correctly, the data might be downloaded if a new account is created, but then again preprocessing steps are missing. 
The relevant GDELT event data is provided.

Hurrican tracks
This is linked to NOAA images, but data collection and preprocessing not reproducible. The relevant Hurricane data is provided.

## Processing
Used ArcGIS Pro and RStudio to explore the data sets and scripts. The GitHub repository contains several data sets (tables, shapefiles) and R scripts, however, their purpose or lineage is not documented and needs to be inferred through exploration and experimentation. The order in which the files have to be run is unclear. The R script needs adjustments for paths. The script Tweets_GDeltCountiesCorrelation.R has a missing library load (spatstat) and once added, still creates an error in line 21 "Error in square(TweetTotal_GdeltTotal) : is.numeric(r) is not TRUE"

## Results

The maps seem impossible to recreate from data without clearer instructions as to how they were created. A solution could be to provide the ArcGIS project files. The boxplots can be reproduced using the R script boxplots.r. It is not entirely clear what the supposed output of the other scripts is. 
