---
title: "Reproducibility review of: An Approach to Assess the Effect of Currentness of Spatial Data on Routing Quality"
author: "Daniel Nüst \\orcid{0000-0002-0024-5046}, Alexander Kmoch \\orcid{0000-0003-4386-4450}"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  pdf_document:
    toc: false
    latex_engine: xelatex
    pandoc_args:
      # https://github.com/chdemko/pandoc-latex-fontsize/wiki
      - '--filter=pandoc-latex-fontsize'
pandoc-latex-fontsize:
  - classes: [smallcontent]
    size: tiny
papersize: a4
header-includes:
  - |
    % https://tex.stackexchange.com/questions/445563/ieeetran-how-to-include-orcid-in-tex-pdf-with-pdflatex/445583 (works with pdflatex)
    \usepackage{scalerel}
    \usepackage{tikz}
    \usetikzlibrary{svg.path}
    \definecolor{orcidlogocol}{HTML}{A6CE39}
    \tikzset{
      orcidlogo/.pic={
        \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
        \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                     svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z     M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                     svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
      }
    }
    \newcommand\orcid[1]{\href{https://orcid.org/#1}{\raisebox{0.15 em}{\mbox{\scalerel*{
    \begin{tikzpicture}[yscale=-1, transform shape]
    \pic{orcidlogo};
    \end{tikzpicture}
    }{|}}}}}
    \definecolor{agileblue}{RGB}{0,77,155}
    \usepackage{url}
urlcolor: agileblue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r logo, eval=TRUE, echo=FALSE, message=FALSE, fig.align='center', out.width='0.3\\linewidth', fig.pos='H'}
temp <- tempfile(fileext = ".pdf")
download.file(url = "https://reproducible-agile.github.io/public/images/reproducible-AGILE-logo-square.pdf", destfile = temp)
knitr::include_graphics(temp)
```

This report is part of the reproducibility review at the AGILE conference.
For more information see [https://reproducible-agile.github.io/](https://reproducible-agile.github.io/).
This document is published on OSF at <TODO>.
To cite the report use

> TODO

# Reviewed paper

> TODO ADD FULL CITATION

# Summary

TODO

# Reviewer notes

The Data and Software Availability section includes references to the GitHub project <https://github.com/mwernerds/agile21_abstaining>, which is the starting point of this reproduction.

```{bash, size="tiny", eval=FALSE}
git clone https://github.com/mwernerds/agile21_abstaining
```

The repository contains a `Dockerfile`, which only installs the also given Python environment description.
I continue with a Python virtual environment:

```{bash, size="tiny", eval=FALSE}
mkvirtualenv agile-004
# all commands below executed in this environment

pip install -r agile21_abstaining/requirements.txt
```

Next, I go through the instructions in the README:

```{bash, size="scriptsize", eval=FALSE}
tar -xjf agile21_abstaining/la.tbz
```

The creates many `.txt` files in a directory `la` with subdirectories `left` and `right`.
I don't run `00_create_public_dataset.py` as this is documented as creating said test data.
Next is the "first experiment" using the file `02_single_classifiers.py`.
In absence of other instructions, I simply try to run it:

```{bash, size="scriptsize", eval=FALSE}
python 02_single_classifiers.py 
```

This prints a number of different training results to the console.
Without a reference, I don't know if these are the correct values tough.

```{.smallcontent}
Loading LA
32266 documents - 2.177MB (training set)
32265 documents - 2.178MB (test set)

Extracting features from the training data using a sparse vectorizer
done in 0.340165s at 6.399MB/s
n_samples: 32266, n_features: 21038

Extracting features from the test data using the same vectorizer
done in 0.323204s at 6.737MB/s
n_samples: 32265, n_features: 21038

================================================================================
Ridge Classifier
________________________________________________________________________________
Training: 
RidgeClassifier(tol=0.01)
train time: 0.300s
test time:  0.001s
accuracy:   0.548
dimensionality: 21038
density: 1.000000

trainig
              precision    recall  f1-score   support

  commercial       0.78      0.78      0.78     16133
 residential       0.78      0.78      0.78     16133

    accuracy                           0.78     32266
   macro avg       0.78      0.78      0.78     32266
weighted avg       0.78      0.78      0.78     32266


================================================================================
Perceptron
________________________________________________________________________________
Training: 
Perceptron(max_iter=50)
train time: 0.142s
test time:  0.002s
accuracy:   0.541
dimensionality: 21038
density: 0.838245

trainig
              precision    recall  f1-score   support

  commercial       0.74      0.77      0.75     16133
 residential       0.76      0.73      0.74     16133

    accuracy                           0.75     32266
   macro avg       0.75      0.75      0.75     32266
weighted avg       0.75      0.75      0.75     32266


================================================================================
Passive-Aggressive
________________________________________________________________________________
Training: 
PassiveAggressiveClassifier(max_iter=50)
train time: 0.276s
test time:  0.001s
accuracy:   0.548
dimensionality: 21038
density: 0.942247

trainig
              precision    recall  f1-score   support

  commercial       0.80      0.78      0.79     16133
 residential       0.79      0.81      0.80     16133

    accuracy                           0.80     32266
   macro avg       0.80      0.80      0.80     32266
weighted avg       0.80      0.80      0.80     32266


================================================================================
MaxEnt
________________________________________________________________________________
Training: 
LogisticRegression(C=0.1, dual=True, multi_class='ovr', n_jobs=1,
                   solver='liblinear')
train time: 0.190s
test time:  0.001s
accuracy:   0.541
dimensionality: 21038
density: 1.000000

trainig
              precision    recall  f1-score   support

  commercial       0.65      0.71      0.68     16133
 residential       0.68      0.63      0.65     16133

    accuracy                           0.67     32266
   macro avg       0.67      0.67      0.67     32266
weighted avg       0.67      0.67      0.67     32266


================================================================================
L2 penalty
________________________________________________________________________________
Training: 
LinearSVC(dual=False, tol=0.001)
train time: 0.877s
test time:  0.002s
accuracy:   0.549
dimensionality: 21038
density: 1.000000

trainig
              precision    recall  f1-score   support

  commercial       0.79      0.80      0.79     16133
 residential       0.80      0.79      0.79     16133

    accuracy                           0.79     32266
   macro avg       0.79      0.79      0.79     32266
weighted avg       0.79      0.79      0.79     32266


________________________________________________________________________________
Training: 
SGDClassifier(max_iter=50)
train time: 0.213s
test time:  0.001s
accuracy:   0.547
dimensionality: 21038
density: 0.962116

trainig
              precision    recall  f1-score   support

  commercial       0.68      0.74      0.71     16133
 residential       0.71      0.65      0.68     16133

    accuracy                           0.69     32266
   macro avg       0.70      0.69      0.69     32266
weighted avg       0.70      0.69      0.69     32266


================================================================================
L1 penalty
________________________________________________________________________________
Training: 
LinearSVC(dual=False, penalty='l1', tol=0.001)
train time: 0.346s
test time:  0.001s
accuracy:   0.546
dimensionality: 21038
density: 0.405552

trainig
              precision    recall  f1-score   support

  commercial       0.76      0.77      0.77     16133
 residential       0.77      0.76      0.76     16133

    accuracy                           0.77     32266
   macro avg       0.77      0.77      0.77     32266
weighted avg       0.77      0.77      0.77     32266


________________________________________________________________________________
Training: 
SGDClassifier(max_iter=50, penalty='l1')
train time: 0.164s
test time:  0.001s
accuracy:   0.540
dimensionality: 21038
density: 0.023054

trainig
              precision    recall  f1-score   support

  commercial       0.57      0.72      0.64     16133
 residential       0.62      0.45      0.52     16133

    accuracy                           0.58     32266
   macro avg       0.59      0.58      0.58     32266
weighted avg       0.59      0.58      0.58     32266


================================================================================
Elastic-Net penalty
________________________________________________________________________________
Training: 
SGDClassifier(max_iter=50, penalty='elasticnet')
train time: 0.177s
test time:  0.001s
accuracy:   0.545
dimensionality: 21038
density: 0.338911

trainig
              precision    recall  f1-score   support

  commercial       0.65      0.72      0.68     16133
 residential       0.68      0.61      0.64     16133

    accuracy                           0.66     32266
   macro avg       0.66      0.66      0.66     32266
weighted avg       0.66      0.66      0.66     32266


================================================================================
NearestCentroid (aka Rocchio classifier)
________________________________________________________________________________
Training: 
NearestCentroid()
train time: 0.006s
test time:  0.005s
accuracy:   0.529
trainig
              precision    recall  f1-score   support

  commercial       0.61      0.69      0.65     16133
 residential       0.64      0.55      0.59     16133

    accuracy                           0.62     32266
   macro avg       0.63      0.62      0.62     32266
weighted avg       0.63      0.62      0.62     32266


================================================================================
Naive Bayes
________________________________________________________________________________
Training: 
MultinomialNB(alpha=0.01)
train time: 0.012s
test time:  0.007s
accuracy:   0.547
/home/daniel/.virtualenvs/agile-004/lib/python3.8/site-packages/sklearn/utils/deprecation.py:101: FutureWarning: Attribute coef_ was deprecated in version 0.24 and will be removed in 1.1 (renaming of 0.26).
  warnings.warn(msg, category=FutureWarning)
dimensionality: 21038
density: 1.000000

trainig
              precision    recall  f1-score   support

  commercial       0.76      0.79      0.78     16133
 residential       0.78      0.75      0.77     16133

    accuracy                           0.77     32266
   macro avg       0.77      0.77      0.77     32266
weighted avg       0.77      0.77      0.77     32266


________________________________________________________________________________
Training: 
BernoulliNB(alpha=0.01)
train time: 0.018s
test time:  0.010s
accuracy:   0.548
/home/daniel/.virtualenvs/agile-004/lib/python3.8/site-packages/sklearn/utils/deprecation.py:101: FutureWarning: Attribute coef_ was deprecated in version 0.24 and will be removed in 1.1 (renaming of 0.26).
  warnings.warn(msg, category=FutureWarning)
dimensionality: 21038
density: 1.000000

trainig
              precision    recall  f1-score   support

  commercial       0.74      0.80      0.77     16133
 residential       0.79      0.71      0.75     16133

    accuracy                           0.76     32266
   macro avg       0.76      0.76      0.76     32266
weighted avg       0.76      0.76      0.76     32266


================================================================================
LinearSVC with L1-based feature selection
________________________________________________________________________________
Training: 
Pipeline(steps=[('feature_selection',
                 SelectFromModel(estimator=LinearSVC(dual=False, penalty='l1',
                                                     tol=0.001))),
                ('classification', LinearSVC())])
train time: 0.391s
test time:  0.003s
accuracy:   0.547
trainig
              precision    recall  f1-score   support

  commercial       0.77      0.78      0.78     16133
 residential       0.78      0.77      0.78     16133

    accuracy                           0.78     32266
   macro avg       0.78      0.78      0.78     32266
weighted avg       0.78      0.78      0.78     3226
```

**Next script.**

```{bash, size="scriptsize", eval=FALSE}
python 03_abstain_la.py
```

Again, a lot of log output which I don't have anything to compare against.
The final bit seems to be relevant:

```
abstained in 31237 of 32265 cases
A = 0.968139
[[  763    44 15326]
 [   39   182 15911]
 [    0     0     0]]
```

------

1. UNCLEAR HOW THE GIVEN ANALYSIS CONTRIBUTES TO THE PAPER, OR HOW SPECIFICC FIGURES FROM THE PAPER CAN BE RECREATED.
2. PAPER MENTIONS OPENSTREETMAP DATA - UNCLEAR HOW THAT WAS CREATED OR WHERE IT IS.
3. DATA AND SOFTWARE AVAILABILIIY - SECTION MENTIONS "OSM DATA EXPORTED.." - WHERE IS IT EXPORTED TO?

# Comments to the authors

- Re. Twitter data sharing: please consider next time storing the IDs of the used Tweets, which allows to recreate the dataset with a tool like [twarc](https://twarc-project.readthedocs.io/)
- The README is not easy to understand, with incomplete sentences in several places and some formatting problems towards the end; I suggest to use the fact that you are multiple co-authors to work through the instructions and improve them from a reader perspective

```{r, echo=FALSE, eval=FALSE, results='hide'}
# create ZIP of reproduction files and upload to OSF
library("zip")
library("here")

zipfile <- here::here("004/agile-reproreview-2021-004.zip")
file.remove(zipfile)
zip::zipr(zipfile,
          c(here::here("004/..")))

library("osfr") # See docs at https://docs.ropensci.org/osfr/
# OSF_PAT is in .Renviron in parent directory
# We cannot use osfr to create a new component (with osfr::osf_create_component(x = osfr::osf_retrieve_node("6k5fh"), ...) because that will set the storage location to outside Europe.

# retrieve project
project <- osfr::osf_retrieve_node("")

# upload files
osfr::osf_upload(x = project,
                 conflicts = "overwrite",
                 path = c(list.files(here::here("PATH"),
                                     pattern = "reproreview-agile.*(pdf$|Rmd$|zip$)",
                                     full.names = TRUE),
                          "COPYRIGHT"
                          )
                 )
```
