---
title: "Reproducibility review of: PAPER TITLE"
author: "TODO \\orcid{0000-0000-0000-TODO}"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  pdf_document:
    toc: false
papersize: a4
header-includes:
  - |
    % https://tex.stackexchange.com/questions/445563/ieeetran-how-to-include-orcid-in-tex-pdf-with-pdflatex/445583 (works with pdflatex)
    \usepackage{scalerel}
    \usepackage{tikz}
    \usetikzlibrary{svg.path}
    \definecolor{orcidlogocol}{HTML}{A6CE39}
    \tikzset{
      orcidlogo/.pic={
        \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
        \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                     svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z     M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                     svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
      }
    }
    \newcommand\orcid[1]{\href{https://orcid.org/#1}{\raisebox{0.15 em}{\mbox{\scalerel*{
    \begin{tikzpicture}[yscale=-1, transform shape]
    \pic{orcidlogo};
    \end{tikzpicture}
    }{|}}}}}
    \definecolor{agileblue}{RGB}{0,77,155}
urlcolor: agileblue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r logo, eval=TRUE, echo=FALSE, message=FALSE, fig.align='center', out.width='0.3\\linewidth', fig.pos='H'}
temp <- tempfile(fileext = ".pdf")
download.file(url = "https://reproducible-agile.github.io/public/images/reproducible-AGILE-logo-square.pdf", destfile = temp)
knitr::include_graphics(temp)
```

This report is part of the reproducibility review at the AGILE conference.
For more information see [https://reproducible-agile.github.io/](https://reproducible-agile.github.io/).
This document is published on OSF at OSF LINK HERE.
To cite the report use

> FULL REPORT CITATION HERE

# Reviewed paper

ADD FULL CITATION

# Summary

- Result of the reproduction
- main outcome or figure

\clearpage

# Reproducibility reviewer notes

- technical details about reproduction
- code snippets
- summary of communication with author
- figures/screenshots
- runtime
- reproduction efforts

```{bash some_code, eval=FALSE, size="scriptsize"}
command line code
```

```{r, echo=FALSE, eval=FALSE, results='hide'}
# create ZIP of reproduction files and upload to OSF
library("zip")
library("here")

zipfile <- here::here("PATH/agile-reproreview-YEAR-NUMBER.zip")
file.remove(zipfile)
zip::zipr(zipfile,
          here::here("2020-018/files to add to the zip, if any"))

library("osfr") # See docs at https://docs.ropensci.org/osfr/
# OSF_PAT is in .Renviron in parent directory
# We cannot use osfr to create a new component (with osfr::osf_create_component(x = osfr::osf_retrieve_node("6k5fh"), ...) because that will set the storage location to outside Europe.

# retrieve project
project <- osfr::osf_retrieve_node("OSF ID")

# upload files
osfr::osf_upload(x = project,
                 conflicts = "overwrite",
                 path = c(list.files(here::here("PATH"),
                                     pattern = "agile-reproreview-.*(pdf$|Rmd$|zip$)",
                                     full.names = TRUE),
                          "COPYRIGHT"
                          )
                 )
```