---
title: "Reproducibility Review Template"
author: "Augusta Authora"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r logo, echo = FALSE, message=FALSE, fig.align='center', out.width='0.3\\linewidth', fig.pos='H'}
temp <- tempfile(fileext = ".pdf")
download.file(url = "https://github.com/reproducible-agile/reproducible-agile.github.io/raw/master/public/images/reproducible-AGILE-logo-square.pdf", destfile = temp)
knitr::include_graphics(temp)
```

# Summary

- Result of the reproduction
- main outcome or figure

# Resources

This document reports on the reproduction of the article _ARTICLE REFERENCE HERE_.

This reproduction report is published on OSF at _OSF LINK HERE_.

The code and data used is available online at _ADD REFERENCES/CITATIONS/LINKS_.

\clearpage

# Reproducibility reviewer notes

- technical details about reproduction
- code snippets
- summary of communication with author
- figures/screenshots
- runtime
- reproduction efforts
