---
title: "Reproducibility review of: PAPER TITLE"
author: "Carlos Granell \\orcid{0000-0003-1004-9695}"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  pdf_document:
    toc: false
papersize: a4
header-includes:
  - |
    % https://tex.stackexchange.com/questions/445563/ieeetran-how-to-include-orcid-in-tex-pdf-with-pdflatex/445583 (works with pdflatex)
    \usepackage{scalerel}
    \usepackage{tikz}
    \usetikzlibrary{svg.path}
    \definecolor{orcidlogocol}{HTML}{A6CE39}
    \tikzset{
      orcidlogo/.pic={
        \fill[orcidlogocol] svg{M256,128c0,70.7-57.3,128-128,128C57.3,256,0,198.7,0,128C0,57.3,57.3,0,128,0C198.7,0,256,57.3,256,128z};
        \fill[white] svg{M86.3,186.2H70.9V79.1h15.4v48.4V186.2z}
                     svg{M108.9,79.1h41.6c39.6,0,57,28.3,57,53.6c0,27.5-21.5,53.6-56.8,53.6h-41.8V79.1z     M124.3,172.4h24.5c34.9,0,42.9-26.5,42.9-39.7c0-21.5-13.7-39.7-43.7-39.7h-23.7V172.4z}
                     svg{M88.7,56.8c0,5.5-4.5,10.1-10.1,10.1c-5.6,0-10.1-4.6-10.1-10.1c0-5.6,4.5-10.1,10.1-10.1C84.2,46.7,88.7,51.3,88.7,56.8z};
      }
    }
    \newcommand\orcid[1]{\href{https://orcid.org/#1}{\raisebox{0.15 em}{\mbox{\scalerel*{
    \begin{tikzpicture}[yscale=-1, transform shape]
    \pic{orcidlogo};
    \end{tikzpicture}
    }{|}}}}}
    \definecolor{agileblue}{RGB}{0,77,155}
urlcolor: agileblue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r logo, eval=TRUE, echo=FALSE, message=FALSE, fig.align='center', out.width='0.3\\linewidth', fig.pos='H'}
temp <- tempfile(fileext = ".pdf")
download.file(url = "https://reproducible-agile.github.io/public/images/reproducible-AGILE-logo-square.pdf", destfile = temp)
knitr::include_graphics(temp)
```

This report is part of the reproducibility review at the AGILE conference.
For more information see [https://reproducible-agile.github.io/](https://reproducible-agile.github.io/).
This document is published on OSF at OSF LINK HERE.
To cite the report use

> FULL REPORT CITATION HERE

# Reviewed paper

> Monika Kopecka, Daniel Szatmári, Juraj Holec and Ján Feranec (2021). Urban heat island modelling based on MUKLIMO: examples from Slovakia. AGILE 2021

# Summary

Results were partially reproducible given special conditions. The main body of the article included a figure (Fig. 2) composed of three line charts. That figure was reproduced based on the data and an excel stylesheet provided by the authors to the repro reviewer (private  email). In the correspondence with authors, they stated that the "data source of the measured temperature depicted on Fig. 2 are the climatological databases of Slovak Hydrometeorological Institute. However these data are not publicly available, they can be provided upon request for fee". This suggest that the input data for Figure 2 cannot be disclosed.   

The article includes four annexes with raster images derived from the execution of the MUKLIMO model. Required model results cannot be disclosed (based on correspondence with authors). Therefore, the article cannot be reproduced by the research community , although the reviewer reproduced parts of the article in confidentiality.

\clearpage

# Reproducibility reviewer notes

This section includes recommendations and suggestions from the rero reviewer that would improve the level of reproducibility of the article.

The article includes a DASA section. Reports the software tools used and the version (for example, MUKLIMO_3, QGIS 3.6.3-Noosa). It also specifies the data layers that are required for some of the analytical steps. The analytical process is narratively described, which is unfortunately not enough to attempt a successful reproduction

To facilitate reproduction, authors are encouraged to check the [AGILE Reproducible Paper Guidelines](https://doi.org/10.17605/OSF.IO/CB7Z8) and consider the following recommendations:

- The explicit registration to any service or platform to access code, tools and/or data must be avoidable. It is recommended to provide easy access to any resources associated with the article without the need for registration.
- The DASA section must include reasons why the code and data cannot be disclosed.
- It is strongly recommended to provide instructions on how to generate the main findings of the article. Typically this takes the form of README files included in public code repositories (eg github), which often also include associated data sets and scripts.
- When the original input data sets cannot be disclosed, it is suggested to provide at least synthetic data or a small part of the original data sets to verify computational workflows.
- When the results are generated by combining multiple data and tools (model, Python scripts, post-processing steps with QGIS, etc.), it is strongly recommended to provide the description (for example, dockerfile) and/or images of the computational environment  required to run the analytical workflow.


```{r, echo=FALSE, eval=FALSE, results='hide'}
# create ZIP of reproduction files and upload to OSF
library("zip")
library("here")

zipfile <- here::here("PATH/agile-reproreview-YEAR-NUMBER.zip")
file.remove(zipfile)
zip::zipr(zipfile,
          here::here("2020-018/files to add to the zip, if any"))

library("osfr") # See docs at https://docs.ropensci.org/osfr/
# OSF_PAT is in .Renviron in parent directory
# We cannot use osfr to create a new component (with osfr::osf_create_component(x = osfr::osf_retrieve_node("6k5fh"), ...) because that will set the storage location to outside Europe.

# retrieve project
project <- osfr::osf_retrieve_node("OSF ID")

# upload files
osfr::osf_upload(x = project,
                 conflicts = "overwrite",
                 path = c(list.files(here::here("PATH"),
                                     pattern = "agile-reproreview-.*(pdf$|Rmd$|zip$)",
                                     full.names = TRUE),
                          "COPYRIGHT"
                          )
                 )
```